Discriminating the Influence of Correlated Factors \\from Multivariate Observations: the Back-to-Back Regression

### 2020-05-18 paper/__latexindent_temp.tex
fmri

@article{cardinali2013data,
  title={Data assimilation: Observation influence diagnostic of a data assimilation system},
  author={Cardinali, C},
  journal={Shinfield Park, England: European Centre for Medium-Range Weather Forecasts: Research Department},
  year={2013}
}

>>>>

@article{fmriprep1,
    author = {Esteban, Oscar and Markiewicz, Christopher and Blair, Ross W and Moodie, Craig and Isik, Ayse Ilkay and Erramuzpe Aliaga, Asier and Kent, James and Goncalves, Mathias and DuPre, Elizabeth and Snyder, Madeleine and Oya, Hiroyuki and Ghosh, Satrajit and Wright, Jessey and Durnez, Joke and Poldrack, Russell and Gorgolewski, Krzysztof Jacek},
    title = {{fMRIPrep}: a robust preprocessing pipeline for functional {MRI}},
    year = {2018},
    doi = {10.1038/s41592-018-0235-4},
    journal = {Nature Methods}
}

@article{fmriprep2,
    author = {Esteban, Oscar and Blair, Ross and Markiewicz, Christopher J. and Berleant, Shoshana L. and Moodie, Craig and Ma, Feilong and Isik, Ayse Ilkay and Erramuzpe, Asier and Kent, James D. andGoncalves, Mathias and DuPre, Elizabeth and Sitek, Kevin R. and Gomez, Daniel E. P. and Lurie, Daniel J. and Ye, Zhifang and Poldrack, Russell A. and Gorgolewski, Krzysztof J.},
    title = {fMRIPrep},
    year = 2018,
    doi = {10.5281/zenodo.852659},
    publisher = {Zenodo},
    journal = {Software}
}

@article{nipype1,
    author = {Gorgolewski, K. and Burns, C. D. and Madison, C. and Clark, D. and Halchenko, Y. O. and Waskom, M. L. and Ghosh, S.},
    doi = {10.3389/fninf.2011.00013},
    journal = {Frontiers in Neuroinformatics},
    pages = 13,
    shorttitle = {Nipype},
    title = {Nipype: a flexible, lightweight and extensible neuroimaging data processing framework in Python},
    volume = 5,
    year = 2011
}

@article{nipype2,
    author = {Gorgolewski, Krzysztof J. and Esteban, Oscar and Markiewicz, Christopher J. and Ziegler, Erik and Ellis, David Gage and Notter, Michael Philipp and Jarecka, Dorota and Johnson, Hans and Burns, Christopher and Manhães-Savio, Alexandre and Hamalainen, Carlo and Yvernault, Benjamin and Salo, Taylor and Jordan, Kesshi and Goncalves, Mathias and Waskom, Michael and Clark, Daniel and Wong, Jason and Loney, Fred and Modat, Marc and Dewey, Blake E and Madison, Cindee and Visconti di Oleggio Castello, Matteo and Clark, Michael G. and Dayan, Michael and Clark, Dav and Keshavan, Anisha and Pinsard, Basile and Gramfort, Alexandre and Berleant, Shoshana and Nielson, Dylan M. and Bougacha, Salma and Varoquaux, Gael and Cipollini, Ben and Markello, Ross and Rokem, Ariel and Moloney, Brendan and Halchenko, Yaroslav O. and Wassermann , Demian and Hanke, Michael and Horea, Christian and Kaczmarzyk, Jakub and Gilles de Hollander and DuPre, Elizabeth and Gillman, Ashley and Mordom, David and Buchanan, Colin and Tungaraza, Rosalia and Pauli, Wolfgang M. and Iqbal, Shariq and Sikka, Sharad and Mancini, Matteo and Schwartz, Yannick and Malone, Ian B. and Dubois, Mathieu and Frohlich, Caroline and Welch, David and Forbes, Jessica and Kent, James and Watanabe, Aimi and Cumba, Chad and Huntenburg, Julia M. and Kastman, Erik and Nichols, B. Nolan and Eshaghi, Arman and Ginsburg, Daniel and Schaefer, Alexander and Acland, Benjamin and Giavasis, Steven and Kleesiek, Jens and Erickson, Drew and Küttner, René and Haselgrove, Christian and Correa, Carlos and Ghayoor, Ali and Liem, Franz and Millman, Jarrod and Haehn, Daniel and Lai, Jeff and Zhou, Dale and Blair, Ross and Glatard, Tristan and Renfro, Mandy and Liu, Siqi and Kahn, Ari E. and Pérez-García, Fernando and Triplett, William and Lampe, Leonie and Stadler, Jörg and Kong, Xiang-Zhen and Hallquist, Michael and Chetverikov, Andrey and Salvatore, John and Park, Anne and Poldrack, Russell and Craddock, R. Cameron and Inati, Souheil and Hinds, Oliver and Cooper, Gavin and Perkins, L. Nathan and Marina, Ana and Mattfeld, Aaron and Noel, Maxime and Lukas Snoek and Matsubara, K and Cheung, Brian and Rothmei, Simon and Urchs, Sebastian and Durnez, Joke and Mertz, Fred and Geisler, Daniel and Floren, Andrew and Gerhard, Stephan and Sharp, Paul and Molina-Romero, Miguel and Weinstein, Alejandro and Broderick, William and Saase, Victor and Andberg, Sami Kristian and Harms, Robbert and Schlamp, Kai and Arias, Jaime and Papadopoulos Orfanos, Dimitri and Tarbert, Claire and Tambini, Arielle and De La Vega, Alejandro and Nickson, Thomas and Brett, Matthew and Falkiewicz, Marcel and Podranski, Kornelius and Linkersdörfer, Janosch and Flandin, Guillaume and Ort, Eduard and Shachnev, Dmitry and McNamee, Daniel and Davison, Andrew and Varada, Jan and Schwabacher, Isaac and Pellman, John and Perez-Guevara, Martin and Khanuja, Ranjeet and Pannetier, Nicolas and McDermottroe, Conor and Ghosh, Satrajit},
    title = {Nipype},
    year = 2018,
    doi = {10.5281/zenodo.596855},
    publisher = {Zenodo},
    journal = {Software}
}

@article{n4,
    author = {Tustison, N. J. and Avants, B. B. and Cook, P. A. and Zheng, Y. and Egan, A. and Yushkevich, P. A. and Gee, J. C.},
    doi = {10.1109/TMI.2010.2046908},
    issn = {0278-0062},
    journal = {IEEE Transactions on Medical Imaging},
    number = 6,
    pages = {1310-1320},
    shorttitle = {N4ITK},
    title = {N4ITK: Improved N3 Bias Correction},
    volume = 29,
    year = 2010
}

@article{fs_reconall,
    author = {Dale, Anders M. and Fischl, Bruce and Sereno, Martin I.},
    doi = {10.1006/nimg.1998.0395},
    issn = {1053-8119},
    journal = {NeuroImage},
    number = 2,
    pages = {179-194},
    shorttitle = {Cortical Surface-Based Analysis},
    title = {Cortical Surface-Based Analysis: I. Segmentation and Surface Reconstruction},
    url = {http://www.sciencedirect.com/science/article/pii/S1053811998903950},
    volume = 9,
    year = 1999
}

@article{mindboggle,
    author = {Klein, Arno and Ghosh, Satrajit S. and Bao, Forrest S. and Giard, Joachim and Häme, Yrjö and Stavsky, Eliezer and Lee, Noah and Rossa, Brian and Reuter, Martin and Neto, Elias Chaibub and Keshavan, Anisha},
    doi = {10.1371/journal.pcbi.1005350},
    issn = {1553-7358},
    journal = {PLOS Computational Biology},
    number = 2,
    pages = {e1005350},
    title = {Mindboggling morphometry of human brains},
    url = {http://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1005350},
    volume = 13,
    year = 2017
}

@article{mni152lin,
    title = {A {Probabilistic} {Atlas} of the {Human} {Brain}: {Theory} and {Rationale} for {Its} {Development}: {The} {International} {Consortium} for {Brain} {Mapping} ({ICBM})},
    author = {Mazziotta, John C. and Toga, Arthur W. and Evans, Alan and Fox, Peter and Lancaster, Jack},
    volume = {2},
    issn = {1053-8119},
    shorttitle = {A {Probabilistic} {Atlas} of the {Human} {Brain}},
    doi = {10.1006/nimg.1995.1012},
    number = {2, Part A},
    journal = {NeuroImage},
    year = {1995},
    pages = {89--101}
}

@article{mni152nlin2009casym,
    title = {Unbiased nonlinear average age-appropriate brain templates from birth to adulthood},
    author = {Fonov, VS and Evans, AC and McKinstry, RC and Almli, CR and Collins, DL},
    doi = {10.1016/S1053-8119(09)70884-5},
    journal = {NeuroImage},
    pages = {S102},
    volume = {47, Supplement 1},
    year = 2009
}

@article{mni152nlin6asym,
    author = {Evans, AC and Janke, AL and Collins, DL and Baillet, S},
    title = {Brain templates and atlases},
    doi = {10.1016/j.neuroimage.2012.01.024},
    journal = {NeuroImage},
    volume = {62},
    number = {2},
    pages = {911--922},
    year = 2012
}

@article{ants,
    author = {Avants, B.B. and Epstein, C.L. and Grossman, M. and Gee, J.C.},
    doi = {10.1016/j.media.2007.06.004},
    issn = {1361-8415},
    journal = {Medical Image Analysis},
    number = 1,
    pages = {26-41},
    shorttitle = {Symmetric diffeomorphic image registration with cross-correlation},
    title = {Symmetric diffeomorphic image registration with cross-correlation: Evaluating automated labeling of elderly and neurodegenerative brain},
    url = {http://www.sciencedirect.com/science/article/pii/S1361841507000606},
    volume = 12,
    year = 2008
}

@article{fsl_fast,
    author = {Zhang, Y. and Brady, M. and Smith, S.},
    doi = {10.1109/42.906424},
    issn = {0278-0062},
    journal = {IEEE Transactions on Medical Imaging},
    number = 1,
    pages = {45-57},
    title = {Segmentation of brain {MR} images through a hidden Markov random field model and the expectation-maximization algorithm},
    volume = 20,
    year = 2001
}

@article{fieldmapless1,
    author = {Wang, Sijia and Peterson, Daniel J. and Gatenby, J. C. and Li, Wenbin and Grabowski, Thomas J. and Madhyastha, Tara M.},
    doi = {10.3389/fninf.2017.00017},
    issn = {1662-5196},
    journal = {Frontiers in Neuroinformatics},
    language = {English},
    title = {Evaluation of Field Map and Nonlinear Registration Methods for Correction of Susceptibility Artifacts in Diffusion {MRI}},
    url = {http://journal.frontiersin.org/article/10.3389/fninf.2017.00017/full},
    volume = 11,
    year = 2017
}

@phdthesis{fieldmapless2,
    address = {Berlin},
    author = {Huntenburg, Julia M.},
    language = {eng},
    school = {Freie Universität},
    title = {Evaluating nonlinear coregistration of {BOLD} {EPI} and T1w images},
    type = {Master's Thesis},
    url = {http://hdl.handle.net/11858/00-001M-0000-002B-1CB5-A},
    year = 2014
}

@article{fieldmapless3,
    author = {Treiber, Jeffrey Mark and White, Nathan S. and Steed, Tyler Christian and Bartsch, Hauke and Holland, Dominic and Farid, Nikdokht and McDonald, Carrie R. and Carter, Bob S. and Dale, Anders Martin and Chen, Clark C.},
    doi = {10.1371/journal.pone.0152472},
    issn = {1932-6203},
    journal = {PLOS ONE},
    number = 3,
    pages = {e0152472},
    title = {Characterization and Correction of Geometric Distortions in 814 Diffusion Weighted Images},
    url = {http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0152472},
    volume = 11,
    year = 2016
}

@article{flirt,
    title = {A global optimisation method for robust affine registration of brain images},
    volume = {5},
    issn = {1361-8415},
    url = {http://www.sciencedirect.com/science/article/pii/S1361841501000366},
    doi = {10.1016/S1361-8415(01)00036-6},
    number = {2},
    urldate = {2018-07-27},
    journal = {Medical Image Analysis},
    author = {Jenkinson, Mark and Smith, Stephen},
    year = {2001},
    keywords = {Affine transformation, flirt, fsl, Global optimisation, Multi-resolution search, Multimodal registration, Robustness},
    pages = {143--156}
}

@article{mcflirt,
    author = {Jenkinson, Mark and Bannister, Peter and Brady, Michael and Smith, Stephen},
    doi = {10.1006/nimg.2002.1132},
    issn = {1053-8119},
    journal = {NeuroImage},
    number = 2,
    pages = {825-841},
    title = {Improved Optimization for the Robust and Accurate Linear Registration and Motion Correction of Brain Images},
    url = {http://www.sciencedirect.com/science/article/pii/S1053811902911328},
    volume = 17,
    year = 2002
}

@article{bbr,
    author = {Greve, Douglas N and Fischl, Bruce},
    doi = {10.1016/j.neuroimage.2009.06.060},
    issn = {1095-9572},
    journal = {NeuroImage},
    number = 1,
    pages = {63-72},
    title = {Accurate and robust brain image alignment using boundary-based registration},
    volume = 48,
    year = 2009
}

@article{aroma,
    author = {Pruim, Raimon H. R. and Mennes, Maarten and van Rooij, Daan and Llera, Alberto and Buitelaar, Jan K. and Beckmann, Christian F.},
    doi = {10.1016/j.neuroimage.2015.02.064},
    issn = {1053-8119},
    journal = {NeuroImage},
    number = {Supplement C},
    pages = {267-277},
    shorttitle = {ICA-AROMA},
    title = {ICA-{AROMA}: A robust {ICA}-based strategy for removing motion artifacts from fMRI data},
    url = {http://www.sciencedirect.com/science/article/pii/S1053811915001822},
    volume = 112,
    year = 2015
}

@article{power_fd_dvars,
    author = {Power, Jonathan D. and Mitra, Anish and Laumann, Timothy O. and Snyder, Abraham Z. and Schlaggar, Bradley L. and Petersen, Steven E.},
    doi = {10.1016/j.neuroimage.2013.08.048},
    issn = {1053-8119},
    journal = {NeuroImage},
    number = {Supplement C},
    pages = {320-341},
    title = {Methods to detect, characterize, and remove motion artifact in resting state fMRI},
    url = {http://www.sciencedirect.com/science/article/pii/S1053811913009117},
    volume = 84,
    year = 2014
}

@article{confounds_satterthwaite_2013,
    author = {Satterthwaite, Theodore D. and Elliott, Mark A. and Gerraty, Raphael T. and Ruparel, Kosha and Loughead, James and Calkins, Monica E. and Eickhoff, Simon B. and Hakonarson, Hakon and Gur, Ruben C. and Gur, Raquel E. and Wolf, Daniel H.},
    doi = {10.1016/j.neuroimage.2012.08.052},
    issn = {10538119},
    journal = {NeuroImage},
    number = 1,
    pages = {240--256},
    title = {{An improved framework for confound regression and filtering for control of motion artifact in the preprocessing of resting-state functional connectivity data}},
    url = {http://linkinghub.elsevier.com/retrieve/pii/S1053811912008609},
    volume = 64,
    year = 2013
}

@article{nilearn,
    author = {Abraham, Alexandre and Pedregosa, Fabian and Eickenberg, Michael and Gervais, Philippe and Mueller, Andreas and Kossaifi, Jean and Gramfort, Alexandre and Thirion, Bertrand and Varoquaux, Gael},
    doi = {10.3389/fninf.2014.00014},
    issn = {1662-5196},
    journal = {Frontiers in Neuroinformatics},
    language = {English},
    title = {Machine learning for neuroimaging with scikit-learn},
    url = {https://www.frontiersin.org/articles/10.3389/fninf.2014.00014/full},
    volume = 8,
    year = 2014
}

@article{lanczos,
    author = {Lanczos, C.},
    doi = {10.1137/0701007},
    issn = {0887-459X},
    journal = {Journal of the Society for Industrial and Applied Mathematics Series B Numerical Analysis},
    number = 1,
    pages = {76-85},
    title = {Evaluation of Noisy Data},
    url = {http://epubs.siam.org/doi/10.1137/0701007},
    volume = 1,
    year = 1964
}

@article{compcor,
    author = {Behzadi, Yashar and Restom, Khaled and Liau, Joy and Liu, Thomas T.},
    doi = {10.1016/j.neuroimage.2007.04.042},
    issn = {1053-8119},
    journal = {NeuroImage},
    number = 1,
    pages = {90-101},
    title = {A component based noise correction method ({CompCor}) for {BOLD} and perfusion based fMRI},
    url = {http://www.sciencedirect.com/science/article/pii/S1053811907003837},
    volume = 37,
    year = 2007
}

@article{hcppipelines,
    author = {Glasser, Matthew F. and Sotiropoulos, Stamatios N. and Wilson, J. Anthony and Coalson, Timothy S. and Fischl, Bruce and Andersson, Jesper L. and Xu, Junqian and Jbabdi, Saad and Webster, Matthew and Polimeni, Jonathan R. and Van Essen, David C. and Jenkinson, Mark},
    doi = {10.1016/j.neuroimage.2013.04.127},
    issn = {1053-8119},
    journal = {NeuroImage},
    pages = {105-124},
    series = {Mapping the Connectome},
    title = {The minimal preprocessing pipelines for the Human Connectome Project},
    url = {http://www.sciencedirect.com/science/article/pii/S1053811913005053},
    volume = 80,
    year = 2013
}

@article{fs_template,
    author = {Reuter, Martin and Rosas, Herminia Diana and Fischl, Bruce},
    doi = {10.1016/j.neuroimage.2010.07.020},
    journal = {NeuroImage},
    number = 4,
    pages = {1181-1196},
    title = {Highly accurate inverse consistent registration: A robust approach},
    volume = 53,
    year = 2010
}

@article{afni,
    author = {Cox, Robert W. and Hyde, James S.},
    doi = {10.1002/(SICI)1099-1492(199706/08)10:4/5<171::AID-NBM453>3.0.CO;2-L},
    journal = {NMR in Biomedicine},
    number = {4-5},
    pages = {171-178},
    title = {Software tools for analysis and visualization of fMRI data},
    volume = 10,
    year = 1997
}

@article{posse_t2s,
    author = {Posse, Stefan and Wiese, Stefan and Gembris, Daniel and Mathiak, Klaus and Kessler, Christoph and Grosse-Ruyken, Maria-Liisa and Elghahwagi, Barbara and Richards, Todd and Dager, Stephen R. and Kiselev, Valerij G.},
    doi = {10.1002/(SICI)1522-2594(199907)42:1<87::AID-MRM13>3.0.CO;2-O},
    journal = {Magnetic Resonance in Medicine},
    number = 1,
    pages = {87-97},
    title = {Enhancement of {BOLD}-contrast sensitivity by single-shot multi-echo functional {MR} imaging},
    volume = 42,
    year = 1999
}

### 2020-05-18 paper/appendix.tex
fmri

>>>>

\begin{wrapfigure}{r}{.5\textwidth}
  \vspace{-11ex}
  \begin{center}
    \includegraphics[width=0.48\textwidth,
                     trim=0cm 0cm 0cm 0cm,
                     clip=True]{figures/fmri_decod.pdf}
    \includegraphics[width=0.48\textwidth,
                     trim=0cm 0cm 0cm 0cm,
                     clip=True]{figures/fmri_betas.pdf}

    \label{fig:fmri_strip}
  \end{center}
  \caption{Top. P-values across subjects derived from a Backward decoding of
  each feature (columns). Bottom. P-values across subjects derived from
  the $\beta$ coefficients of a Forward Model and the $\hat E$ of an unbiased
  B2B (i.e. B2B where $H$ is not regularized). Each cell displays the left
  hemisphere view laterally (top) or ventrally (bottom)}
  \vspace{-6ex}
\end{wrapfigure}

### 2020-05-18 paper/meg_exps.tex
fig
fmri

Next, we apply our method to brain imaging data from the anonymized multimodal
neuroimaging ``Mother Of all Unification Studies'' (MOUS) dataset
\citep{schoffelen2019204}. The dataset contains magneto-encephalography (MEG)
recordings of 102 healthy native-Dutch adults who participated in a reading
task. Twelve subjects were excluded from the analysis because of corrupted file headers.
%
Subjects were exposed to a rapid serial visual presentation of Dutch words. The
word lists consisted of 120 sentences, and scrambled lists of the same words.
Each word was presented on the computer screen for 351ms on average (min: 300ms,
max: 1400ms). Successive words were separated by a blank screen for 300ms, and
successive sentences were separated by an empty screen for a few (3-4) seconds.

@@

@@

\subsubsection{Feature definition}

We aim to identify the word features that cause a variation in brain responses.
We consider four distinct but linearly-correlated features.
%
First, 'Word Length' refers to the total number of letters. Word Length is
expected to specifically cause a variation in the early evoked MEG responses
(i.e. from 100 ms after stimulus onset) elicited by the retinotopically-tuned
visual cortices (e.g. \citep{pegado2014timing}.).
%
Second, 'Word Frequency' indexes how frequently each word appears in Dutch and
was derived with the the Zipf logarithmic scale of \citep{van2014subtlex}
provided by the WordFreq package \citep{speerwordfreq}. Word Frequency is
expected to specifically cause a variation in the late evoked MEG responses
(i.e. from 400 ms), because it variably engages semantic processes in the
temporal cortices \citep{kutas2011thirty}.
%
Third, 'Word Function' indicates whether each word is a content word (i.e. a
noun, a verb, an adjective or an adverb) or a function word (i.e. a preposition,
a conjunction, a determinant, a pronoun or a numeral), and was derived from
Spacy's part of speech tagger \citep{spacy2}. To our knowledge, this feature has
not been thoroughly investigated with MEG. Its causal contribution to reading
processes in the brain thus remains unclear.
%
Finally, to verify that B2B and other methods would not inadequately identify
non-causal features, we added a dummy feature, constructed from a noisy
combination of Word Length and Word Frequency: $dummy = z(length) + z(frequency)
+ \mathcal{N}$, where $z$ normalizes features and $\mathcal{N}$ is a random
vector sampling Gaussian distribution (all terms thus have a zero-mean and a
unit-variance). This procedure yields an $X \in \mathbb{R}^{n \times d_x}$
matrix of $n\approx$ 2,700 words by $d_x=4$ features for each subject. Each of
the columns of $X$ is normalized to have a mean and a standard deviation of 0
and 1 respectively.

\subsubsection{Models and statistics}

We compare B2B to four standard methods: Forward regression, Backward
regression, CCA and PLS, as implemented in scikit-learn \citep{sklearn} and
\citep{bilenko2016pyrcca}, and optimized with nested cross-validation over
twenty $l2$ regularization parameters logarithmically spaced between $10^{-4}$
and $10^4$ (for regression and CCA methods) or 1 to 4 canonical components (for
PLS).

We used the feature importance described in Algorithm \ref{algorithm:b2b_fi} to
assess the extent to which each feature $X_i$ specifically improves the
prediction of held-out $Y$ data, using a five-fold cross-validation (with shuffled
trials to homogeneize the distributions between the training and testing
splits).

Each model was implemented for each subject and each time sample independently.
Pairwise comparison between models were performed using a two-sided Wilcoxon
test across subjects (n=90) using the average $\Delta R$ across time.
Corresponding effect sizes are shown in Figure~\ref{fig:meg_results}, and
p-values are reported below.

@@

\begin{wrapfigure}{r}{.6\textwidth}
  %\vspace{-12ex}
  \begin{center}
    \includegraphics[width=0.6\textwidth, trim=0cm 0cm 0cm 0cm, clip=True]{figures/meg.pdf}
  \end{center}
  %\vspace{-5ex}
  \caption{Multiple models (color-coded) are compared on their ability to
  reliably predict single-trial MEG signals evoked by words. Left. Average
  improvement of correlation coefficient $\Delta R$ for each of the four
  features (rows). Error bars indicate standard error of the mean (SEM) across
  subjects. Right. Average $\Delta R$ across time for each subject (dots). Top
  horizontal lines indicate when B2B significantly outperforms other methods
  (red) and vice versa. \label{fig:meg_results}
}
\end{wrapfigure}

>>>>

@@

We use the same features as for the fMRI experiments, except that the features
were not convolved by an hemodynamic response function. This yields an $X \in \mathbb{R}^{n \times d_x}$
matrix of $n\approx$ 2,700 words by $d_x=4$ features for each subject. Each of
the columns of $X$ is normalized to have a mean and a standard deviation of 0
and 1 respectively.

We compare B2B against other methods following the same procedure as for the
fMRI experiments, except that the search light is applied across time samples.

@@

\begin{figure}
  %\vspace{-12ex}
  \begin{center}
    \includegraphics[width=0.6\textwidth,
                     trim=0cm 0cm 0cm 0cm, clip=True]{figures/meg.pdf}
  \end{center}
  %\vspace{-5ex}
  \caption{Multiple models (color-coded) are compared on their ability to
  reliably predict single-trial MEG signals evoked by words. Left. Average
  improvement of correlation coefficient $\Delta R$ for each of the four
  features (rows). Error bars indicate standard error of the mean (SEM) across
  subjects. Right. Average $\Delta R$ across time for each subject (dots). Top
  horizontal lines indicate when B2B significantly outperforms other methods
  (red) and vice versa. \label{fig:meg_results}
}
\end{figure}

@@

### 2020-05-18 paper/paper.tex
fmri

\begin{abstract}
Identifying causes solely from observations can be particularly challenging when
i) potential factors are difficult to manipulate independently and ii)
observations are multi-dimensional. To address this issue, we
introduce ``Back-to-Back'' regression (B2B), a linear method designed to efficiently
measure, from a set of correlated factors, those that most plausibly account for
multidimensional observations. First, we prove the consistency of B2B, its links to
other linear approaches, and show how it provides a robust, unbiased and
interpretable scalar estimate for each factor.
Second, we use a variety of simulated data to show that B2B outperforms
least-squares regression and cross-decomposition techniques (e.g. canonical
correlation analysis and partial least squares) on causal identification when
the factors and the observations are partially collinear.
Finally, we apply B2B to magneto-encephalography of 102 subjects
recorded during a reading task to test whether our method appropriately disentangles
the respective contribution of word length and word frequency - two correlated
factors known to cause early and late brain responses respectively. The results
show that these two factors are better disentangled with B2B than with
other standard techniques.
\end{abstract}

\begin{keyword}
  Cross-Decomposition \sep
  Feature Discovery \sep
  Magnetoencephalography \sep
  Decoding \sep
  Encoding \sep
  Reading \sep
  N400
\end{keyword}

@@

\subsection{Synthetic data}
\label{sec:experiment_synthetic}

\input{synthetic.tex}
\input{meg_exps.tex}

\subsection{Magnetoencephalography data}
\label{sec:experiment_real}

>>>>

\begin{abstract}
Identifying causes solely from observations can be particularly challenging when
i) potential factors are difficult to manipulate independently and ii)
observations are multi-dimensional. To address this issue, we
introduce ``Back-to-Back'' regression (B2B), a linear method designed to efficiently
measure, from a set of correlated factors, those that most plausibly account for
multidimensional observations. First, we prove the consistency of B2B, its links to
other linear approaches, and show how it provides a robust, unbiased and
interpretable scalar estimate for each factor.
Second, we use a variety of simulated data to show that B2B outperforms
least-squares regression and cross-decomposition techniques (e.g. canonical
correlation analysis and partial least squares) on causal identification when
the factors and the observations are partially collinear.
Finally, we apply B2B to magneto-encephalography and fMRI of 102 subjects
recorded during a one hour long reading task to test whether our method appropriately disentangles
the respective contribution of word length and word frequency - two correlated
factors known to cause early visual and late associative cortical responses respectively. The results
show that these two factors are better disentangled with B2B than with
other standard techniques.
\end{abstract}

\begin{keyword}
  Cross-Decomposition \sep
  Feature Discovery \sep
  Magnetoencephalography \sep
  fMRI \sep
  Decoding \sep
  Encoding \sep
  Reading \sep
\end{keyword}

@@

\subsection{Synthetic data}
\label{sec:experiment_synthetic}
\input{synthetic.tex}

\subsection{functional Magnetic Resonance Imaging}
\label{sec:experiment_fmri}
\input{fmri_exps.tex}

\subsection{Magnetoencephalography}
\label{sec:experiment_real}
\input{meg_exps.tex}
